Test susieI using chr17 to 22

### 2020-08-19 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
more iterations

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
tag <- '20200813-1-1'
Niter <- 10
```

@@

for (i in 1:Niter){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(lapply(gene.rpiplist, "mean"))
  ngdf[, paste("Prior.SNP", i)] <- unlist(lapply(snp.rpiplist, "mean"))
}
ngdf
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
tag <- '20200813-1-1'
Niter <- 50
```

@@

for (i in seq(1, Niter, 10)){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(lapply(gene.rpiplist, "mean"))
  ngdf[, paste("Prior.SNP", i)] <- unlist(lapply(snp.rpiplist, "mean"))
}
ngdf
```
